Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-05-31 supp_mat_complexity_selection.Rmd
updating model selection

get_insect_FL.df <- function(FL){
  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
}
```

>>>>

get_insect_FL.df <- function(FL){
  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
}

overdisp_fun <- function(model) {
  ## number of variance parameters in 
  ##   an n-by-n variance-covariance matrix
  vpars <- function(m) {
    nrow(m)*(nrow(m)+1)/2
  }
  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
  rdf <- nrow(model.frame(model))-model.df
  rp <- residuals(model,type="pearson")
  Pearson.chisq <- sum(rp^2)
  prat <- Pearson.chisq/rdf
  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
}
```

```{r}
# convert treatment to factor to use as 'by' variable in gamm.model
gall_selection.df <- gall_selection.df %>%
  mutate(Treatment_contr.sum=factor(Treatment.focus), 
         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
         sc.clutch_size = as.numeric(scale(gall_individuals)),
         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
# Inspect contrasts:
contrasts(gall_selection.df$Treatment_contr.sum)

## AIC MODEL SELECTION
# Note that I use gamm4 to fit all models to maintain consistency

## GAMM full
m1 <- gamm.model(gall_survival ~ Treatment_contr.sum +
                   s(sc.gall_size, by=Treatment_contr.sum) + 
                   s(sc.clutch_size, by=Treatment_contr.sum) + 
                   s(sc.female_preference, by=Treatment_contr.sum) + 
                   sc.gall_size:sc.clutch_size + sc.gall_size:sc.clutch_size:Treatment_contr.sum +
                   sc.gall_size:sc.female_preference + sc.gall_size:sc.female_preference:Treatment_contr.sum +                                 sc.clutch_size:sc.female_preference + sc.clutch_size:sc.female_preference:Treatment_contr.sum,
                 data = gall_selection.df)
summary(m1$gam); summary(m1$mer)

gamm_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
                             s(sc.gall_size) + 
                             s(sc.clutch_size, by=Treatment_contr.sum) + 
                             s(sc.female_preference, by=Treatment_contr.sum),
                 data = gall_selection.df)
summary(gamm_reduced$gam); summary(gamm_reduced$mer)

gamm_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum +
                             sc.gall_size + 
                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
                             s(sc.female_preference, by=Treatment_contr.sum),
                 data = gall_selection.df)
summary(gamm_reduced2$gam); summary(gamm_reduced2$mer)

GLMM_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
                             sc.gall_size + 
                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
                             sc.female_preference + sc.female_preference:Treatment_contr.sum,
                            data = gall_selection.df)
summary(GLMM_reduced$gam); summary(GLMM_reduced$mer)

AIC(m1$mer, gamm_reduced$mer, gamm_reduced2$mer, GLMM_reduced$mer)

glmer_reduced <- glmer(gall_survival ~ Treatment_contr.sum +
                             sc.gall_size + 
                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
                             sc.female_preference + sc.female_preference:Treatment_contr.sum +
                             (1|Genotype/Plant_Position/Gall_Number),
                       family=binomial(link=logit),
                       data = gall_selection.df, glmerControl(optimizer="bobyqa"))
summary(glmer_reduced)
overdisp_fun(glmer_reduced) # no evidence of overdispersion

v <- visreg(fit, 'Days', 'Subject', re.form=(~Days|Subject), plot=FALSE)
plot(v)
plot(v, overlay=TRUE)

test <- visreg(glmer_reduced, xvar=c("sc.gall_size"), by="Genotype", re.form=(~1|Genotype), plot=FALSE, 
       scale="response", partial=TRUE, gg=TRUE, overlay=TRUE,
       cond = list(sc.gall_size=0, sc.clutch_size=0, sc.female_preference=0))
plot(test, partial=TRUE, overlay=TRUE)
visreg(glmer_reduced, xvar=c("sc.gall_size"), scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
visreg(glmer_reduced, xvar=c("sc.clutch_size"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
visreg(glmer_reduced, xvar=c("sc.female_preference"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)

## GLMER full
glmer_full <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
                           Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
                         data = gall_selection.df)
summary(glmer_full$gam); summary(glmer_full$mer)
round(vcov(glmer_full$mer), 2) # no evidence of correlations that would confound interpretations of statistical main and interaction effects.

glmer_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) +
                           I(sc.gall_size^2) + I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
                         data = gall_selection.df)
summary(glmer_reduced$gam); summary(glmer_reduced$mer, correlation=TRUE)
visreg(glmer_reduced$gam, xvar="sc.gall_size", by="sc.clutch_size", scale="response")

glmer_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum*sc.clutch_size + sc.gall_size + sc.female_preference +
                               I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
                         data = gall_selection.df)
summary(glmer_reduced2$gam); summary(glmer_reduced2$mer)

AIC(glmer_full$mer, glmer_reduced$mer, glmer_reduced2$mer)

## LMER full
m3 <- gamm4(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)),
            family = gaussian(link=identity),
            random = ~(1|Genotype/Plant_Position/Gall_Number),
            data = gall_selection.df)

AIC(m1$mer, m2$mer, m3$mer) # suggests that the GLMM is best

## Do we need a model with interactions between traits?
m4 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
                 data = gall_selection.df)
AIC(m2$mer, m4$mer) # AIC suggests not

## Do we need a model with non-linear trait effects?
m5 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
                   (I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
                 data = gall_selection.df)
AIC(m4$mer, m5$mer) # 
summary(m5$gam)
summary(m5$mer)

m6 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference), 
                 data = gall_selection.df)
AIC(m5$mer, m6$mer) 
```
